
********
# Exploratory Text Analysis

Workshop by [Sarah Stanley](https://twitter.com/sarcathtic) and Carolyn Moritz  
*Forthcoming*

********

# Intro to RMarkdown
Percolator session by Carolyn Moritz  
*2017/03/01*

The following begins with a handy reference provided by RStudio. To create the basis of demonstration as an independent RMarkdown document: **File** -> **New File** -> **R Markdown...**  
Additions resulting from the Percolator session will be indicated below in <span style="color:green">green</span>.

### Initial Setup
To follow along on your own machine, first install [R](https://cran.r-project.org/) and [RStudio](https://www.rstudio.com/products/rstudio/).  
In the RStudio console, install the RMarkdown package and call the library: 
<br><br>
`install.packages("rmarkdown")`  
`library(rmarkdown)`  

**Reference Links**  
* [Get Started](http://rmarkdown.rstudio.com/lesson-1.html)  
* [RMarkdown Reference Guide](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf)  
* [RMarkdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf)  
* [Gallery](http://rmarkdown.rstudio.com/gallery.html)  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### RMarkdown

This is an RMarkdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

### Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

<span style="color:green">Demonstration: Pushing to site</span>
